\cvsection{Technical Skills}

\textbf{Most Experience:}
Angular,  C++ ,  Python ,  JavaScript , Typescript ,  Git ,  VSTS ,  C ,  SQL , Agile Development ,  HTML ,  CSS ,  Bash ,  Data Structures \& Algo \\
\textbf{Some Experience:}
Java ,  .NET WEB API ,  Android SDK ,  Firebase ,  C\# ,  \LaTeX\  ,  React\\
\textbf{Familiar:}
MATLAB ,  SPSS 



%\cvsection{Areas of Interest}
%
%\begin{itemize}
%    \item Mathematical Physics;
%    \item Quantum Fields and Strings;
%    \item QFT in Curved Spacetime;
%    \item Quantum Gravity.
%\end{itemize}
%
%\cvsection{More Information}
%
%\cvachievement{\faChain}{Academic Record}{\url{http://fma.if.usp.br/~nickolas/summary.pdf}}
%
%\sidedivider
%
%\cvachievement{\faChain}{Lattes CV}{\url{http://lattes.cnpq.br/4933609438452718}}

\cvsection{Education}

\cveventsameline{Bachelor of Technlogy (B.Tech.) \\Mathematics And Computing}{Delhi Technological University (Formerly DCE)}{2014 -- 2018}{Delhi}
\begin{itemize}
\item  CGPA: 8.87
\end{itemize}

\sidedivider

\cveventsameline{}{New Green Field School , Saket}{2010 -- 2014}{Delhi}
\begin{itemize}
\item AISSCE Class XII, Percentage: 94.4 (100 \% in Mathematics)
\item AISSE Class X, CGPA: 9.4
\end{itemize}
%
%\cvsideevent{Gold Metal at the Mathematical Kangaroo Brazil}{Association Kangourou Sans Frontières}{2015}{Brazil}
%
%\sidedivider
%
%\cvsideevent{Honorable Mention at the Brazilian Physics Olympiad}{Brazilian Physical Society}{2013}{Brazil}
%
%\sidedivider
%
%\cvsideevent{Bronze Medal at the Grande ABC's Mathematics Olympiad}{Methodist University of São Paulo}{2011}{São Bernardo do Campo, Brazil}



\cvsection{Projects}

\cveventsameline{}{SMART SPEAKER}{}{}
 A type of \textbf{wireless speaker} and voice command device with an integrated tools and services that offers \textbf{interactive actions and hands-free activation} with the help of one "hot word" (or several "hot words"). The key features were \textbf{solving mathematical expressions, real-time object detection and Image captioning}.
\begin{itemize}
 \item Uses MatBot API (Also developed by Me) to \textbf{solve Mathematical Queries}.
 \item Developed an independent hardware using Raspberry Pi.
 \item Developed an\textbf{ interface between the hardware and software} using secure shell access through laptop and later configured to accept inputs by buttons.
 \item Configured General Purpose Input/output pins on the raspberry pi which allowed to control the scripts by the simple press of a button.
 \item Added \textbf{Text-to-speech and Speech-to-Text} capability for visually impaired people.
\end{itemize}
\sidedivider

\cveventsameline{}{MATBOT}{}{}
A python based assistant or bot which \textbf{solves mathematical expressions, interacts with a human} and support in their day-to-day tasks.
\begin{itemize}
 \item developed Brain for MatBot using NLTK, Scikit on Python.
 \item exposed engine via \textbf{web service based on Flask framework}.
 \item developed MatBot interface on \textbf{Android mobile}.
\end{itemize}
\sidedivider

\cveventsameline{}{DTU CONNECT}{}{}
\begin{itemize}
 \item Developed an Android application to \textbf{ locate potential blood donors} in the event of an accident, within the DTU campus.
 \item Used JSON format to store information about Blood Donors of DTU.
\end{itemize}